Increased Education Level of Women Associates with Higher Occupational Prestige and Happiness

### 2023-03-16 outputs/paper/paper.qmd
added citation

The overall trend of the plot shows a positive upward trajectory in women's education levels over the years, with fluctuations. As shown in @fig-1, the vertical axis shows the percentage of mean education level, while the horizontal axis displays the years.The data reveals significant fluctuations in the mean education level of women over the years, with the education levels gradually increasing over time. The overall increase from 2000 to 2021 is from 13.0 to 13.7.In particular, the mean education level percentage rose from 13.0 to 13.6 between 2000 and 2004, declined in 2006, and has been rising ever since. Overall, this trend highlights the potential benefits of providing access to education for women and demonstrates the need to continue investing in education to ensure that women can reach their full potential and the need to address the barriers that still exist to achieve gender equality in education.

@@

Figure 1 shows an increase in mean highest education level, Figure 2 shows an increase in mean occupational prestige percentage and Figure 3 shows an increase in overall happiness. This means that at a slow and steady rate, women are acquiring better education, getting better jobs and becoming happier. The findings show that there is a positive relationship between job prestige, education and happiness.

@@

According to the UNICEF (citation), the education of girls enhances economies and mitigates inequality, promoting more stable and resilient societies that offer all individuals, including boys and men, the chance to reach their full potential.Over the past two decades, there has been a steady increase in women's education levels, as evidenced by Figure 1, which displays a positive upward trajectory in women's education levels over time. This trend can be attributed to several factors.

>>>>

The overall trend of the plot shows a positive upward trajectory in women's education levels over the years, with fluctuations. As shown in @fig-1, the vertical axis shows the percentage of mean education level, while the horizontal axis displays the years.The data reveals significant fluctuations in the mean education level of women over the years, with the education levels gradually increasing over time. The overall increase from 2000 to 2021 is from 13.0 to 13.7. In particular, the mean education level percentage rose from 13.0 to 13.6 between 2000 and 2004, declined in 2006, and has been rising ever since. Overall, this trend highlights the potential benefits of providing access to education for women and demonstrates the need to continue investing in education to ensure that women can reach their full potential and the need to address the barriers that still exist to achieve gender equality in education.

@@

Figure 1 shows an increase in mean highest education level, Figure 2 shows an increase in mean occupational prestige percentage and Figure 3 shows an increase in overall happiness. This means that at a slow and steady rate, women are acquiring better education, getting better jobs and becoming happier. The findings show that there is a positive trend for job prestige, education and happiness, and suggest they may all be related.

@@

According to the World Bank [@citeWorldBank], the education of girls enhances economies and mitigates inequality, promoting more stable and resilient societies that offer all individuals, including boys and men, the chance to reach their full potential. Over the past two decades, there has been a steady increase in women's education levels, as evidenced by Figure 1, which displays a positive upward trajectory in women's education levels over time. This trend can be attributed to several factors.
